Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-14 gnd_dn_lambda.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article
[referee] 2nd round pass
[referee] version resubmitted to prb.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_gnd_dn_lambda.pdf}
\caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions. The width of the strip is $\pi$ due to folding. We unfold the cylinder and the new stripe have $N$ and $D$ boundary conditions on the left and right plus a $\lambda$ junction in the middle. }
\label{fig:Fig_gnd_dn_lambda}
\end{figure}

@@

The normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as orthonormal basis in the mode expansion, we thus have the 
\begin{equation}
\label{eq:H_in_gnd_dn_lambda}
H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  \left(a^{\dagger}_n a_n + \frac{1}{2} \right) ,
\end{equation}
where the momentum $k$ is defined in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, and the creation and annihilation operators defined as usual
\begin{equation}
\begin{aligned}
a_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  \right) ,\\
a^{\dagger}_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  \right) .\\
\end{aligned}
\end{equation}

The Casimir energy is the vacuum energy brought up by the finite size of the setup. From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and use $x\equiv \frac{\theta}{\pi}$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
\begin{equation}
\begin{aligned}
E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} \left( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  \right) \\  
&= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  +   x^{-s} \Big]\Big|_{s = -1} \\
&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, x ) +  x \right] \\
&= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right),
\end{aligned}
\end{equation}
where we used the fact that the unfolded geometry has length $L=2\pi$. Thus the free energy in the large $\beta$ limit is
\begin{equation}
F = \beta E_c = - \frac{\beta}{2} B_2( x) ,
\end{equation}
which agrees with the boundary state calculation in Sec.~\ref{app:lambda_12}.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_gnd_dn_lambda.pdf}
\caption{Partition function of Hamiltonian with DN and $\lambda$ boundary conditions. We unfold the cylinder and the new stripe have N and D boundary conditions on the top and bottom plus a $\lambda$ junction in the middle. The length $L$ here is the height of the unfolded cylinder $2\pi$. }
\label{fig:Fig_gnd_dn_lambda}
\end{figure}

@@

The normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as an orthonormal basis in the mode expansion, we thus have
\begin{equation}
\label{eq:H_in_gnd_dn_lambda}
H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  \left(a^{\dagger}_n a_n + \frac{1}{2} \right) ,
\end{equation}
where the momentum $k$ is defined in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, and the creation and annihilation operators defined as usual
\begin{equation}
\begin{aligned}
a_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  \right) ,\\
a^{\dagger}_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  \right) .\\
\end{aligned}
\end{equation}

The Casimir energy is the vacuum energy brought up by the finite size of the setup. From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and using $x\equiv \frac{\theta}{\pi}$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
\begin{equation}
\begin{aligned}
E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} \left( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  \right) \\
&= \frac{\pi}{2L} \Bigg( \sum_{n\ge 0 }  ( n + x ) + \sum_{n< 0 }  ( -n - x )  \\
&\quad \quad + \sum_{n \le 0}  (- n + x ) + \sum_{n > 0} ( n- x )  \Bigg) \\
&= \frac{\pi}{2L} \left( 2\sum_{n\ge 0 }  ( n + x ) + 2\sum_{n > 0} ( n- x )  \right).
\end{aligned}
\end{equation}
We use Hurwitz zeta function
\begin{equation}
\zeta_{\rm H}(s,x) = \sum_{n=0}^\infty\frac{1}{(n+x)^s}
\end{equation}
to regularize the sum, 
\begin{equation}
\begin{aligned}
E_c &= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  -  (-x)^{-s} \Big]\Big|_{s = -1} \\
&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, -x ) +  x \right] \\
&= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right),
\end{aligned}
\end{equation}
where in the last line we use $L = 2\pi$ for the unfolded geometry.

Thus the free energy in the large $\beta$ limit is
\begin{equation}
F = \beta E_c = - \frac{\beta}{2} B_2( x) ,
\end{equation}
which agrees with the boundary state calculation in Sec.~\ref{app:lambda_12}.

### 2017-10-14 intro.tex
[referee] version resubmitted to prb.

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the conformal symmetry. Simply put, the interface scatters the otherwise independent modes and therefore demonstrates novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions can exhibit different critical exponents from their bulk counterparts\cite{cardy_conformal_1984}. One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of a boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}. The ``cut-and-join" quench protocol is a popular framework for investigating the spreading of the influence from the localized impurity (or boundary) across the system. As shown in the left panel of Fig.~\ref{fig:cut-and-join}, the system consists of two critical chains A and B, which were prepared in the ground states. They will be joined at $t = 0$ and evolve. Various quantities can be used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem A, when both A and B are identical critical systems. The authors ascribe such increase to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in the topological phase. In this model, the Majorana zero mode acts as a bcc operator and its conformal dimension appears in the exponent of the power law decay of the Loschmidt echo.

@@

In this paper, we generalize these ideas to an interface that interpolate between the total reflective and complete transparent ones. This kind of interface can have many realizations. They can be produced by connecting two different bosonic CFTs in the ``cut-and-join" protocol. As discussed in Ref.~\onlinecite{bachas_permeable_2002}, such interface is a domain wall between two free compact boson theories with different compactification radii. It can also be implemented by non-compact free boson/free fermion on the lattice with a finely tuned bond interaction between the boundary sites (see \onlinecite{peschel_exact_2012,sakai_entanglement_2008} for their entanglement property studies). In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the case of compact boson $\lambda$ is controlled by the ratio of the compactification radii, while for free lattice boson it is controlled by the ratio of masses. We expect it to be tunable in a realistic experimental setting.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
We compute the Loschmidt echo to extract information in the dynamics of the quench process of these models. The Loschmidt echo is the (square of) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$. It decays with a power law $t^{- \alpha}$ for the lack of length scale in the $t \rightarrow \infty$ limit. The decay exponent $\alpha$ has been calculated for various geometries and combinations of the normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs. We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transition coefficients. Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. The finite size fidelity calculation further supports these results.

@@

This paper includes several appendices for technical details. In App.~\ref{app:lambda_12}, we present the leading order analytical calculation of the free energy for the above-mentioned interfaces. In App.~\ref{app:gnd_dn_lambda}, we illustrate an alternative approach with one setup as an example. In App.~\ref{app:F_correction}, we point out two corrections to the free energy, which are complementary to the argument made in the main text. Up to this point, we work exclusively with the oscillator modes of the free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of compactified bosons will \emph{not} contribute to the free energy at the leading order. Therefore, the results remain valid in the physical situation of connecting two compactified bosons of different radii. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation are presented in App.~\ref{app:comp_fid_echo}.

>>>>

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of the physical boundary and isolated impurity weakly break the conformal symmetry. Simply put, the interface scatters the otherwise independent modes and therefore demonstrates novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing (bcc) operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions can exhibit different critical exponents from their bulk counterparts\cite{cardy_conformal_1984}. One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of a boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problems of this kind that have been studied in the last few decades, such as the magnetic impurity in the spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity\cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}. The ``cut-and-join" quench protocol is a popular framework for investigating the spreading of the influence from the localized impurity (or boundary) across the system. As shown in the left panel of Fig.~\ref{fig:cut-and-join}, the system consists of two critical chains A and B, which were prepared in the ground states. They will be joined at $t = 0$ and evolve. Various quantities can be used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of the entanglement entropy in subsystem A, when both A and B are identical critical systems. The authors ascribe such increase to the proliferation and propagation of the quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in the topological phase. In this model, the Majorana zero mode acts as a bcc operator and its conformal dimension appears in the exponent of the power law decay of the Loschmidt echo.

@@

In this paper, we generalize these ideas to an interface that interpolates between the totally reflective and complete transparent ones. This kind of interface can have many realizations. As discussed in Ref.~\onlinecite{bachas_permeable_2002}, one can connect two different bosonic CFTs in the ``cut-and-join" protocol, and the interface is a domain wall between two free compact boson theories with different compactification radii. Such permeable interface can also be implemented by non-compact free boson/fermion on a lattice with a fine-tuned bond interaction between the boundary sites (see \onlinecite{peschel_exact_2012,sakai_entanglement_2008} for their entanglement property studies). In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the case of compact boson, $\lambda$ is controlled by the ratio of the compactification radii, while for the free lattice boson it is controlled by the ratio of masses. We expect it to be tunable in a realistic experimental setting.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
We compute the Loschmidt echo to extract information in the dynamics of the quench process of these models. The Loschmidt echo is the (square of) overlap of the wavefunctions before the quench and the wavefunction evolved for some time $t$. It decays with a power law $t^{- \alpha}$ for the lack of length scale in the $t \rightarrow \infty$ limit. The decay exponent $\alpha$ has been calculated for various geometries and combinations of the normal boundary conditions of the same CFTs in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. We extend the analysis to the aforementioned parametric interface of (possibly) different CFTs. We will see that there are two categories of the scattering matrices $S(\theta)$ of the interfaces, whose scattering angle parameter $\theta$ is determined by the transmission coefficients. Our analytic and numerical results show that $\alpha$ has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. The finite size fidelity calculation further supports these results.

@@

This paper includes several appendices for technical details. In App.~\ref{app:lambda_12}, we present the leading order analytical calculation of the free energy for the setups in Sec.~\ref{sec_sub:analy_eval}. In App.~\ref{app:gnd_dn_lambda}, we illustrate an alternative approach with one setup as an example. In App.~\ref{app:F_correction}, we point out two corrections to the free energy, which are complementary to the argument made in the main text. Up to this point, we work exclusively with the oscillator modes of the free bosons. In App.~\ref{app:compact_diff_boson}, it is shown that the winding modes of the compactified bosons will \emph{not} contribute to the free energy at the leading order. Therefore, the results remain valid in the physical situation of connecting two compactified bosons of different radii. In App.~\ref{app:pf_of_id}, we prove one identity that will be used repeatedly in the analytical evaluation. We derive the scale invariant interface for free bosonic lattice in App.~\ref{app:interface_free_boson}. The details of numerical simulation are presented in App.~\ref{app:comp_fid_echo}.

### 2017-10-14 num_result.tex
[referee] version resubmitted to prb.

We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results. Our numerical evaluations is based on a boson Bogoliubov transformation and the explicit form of the groundstates. The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details. In all the figures, we present the coefficients of the logarithmic term $\frac{\mathcal{F}}{\ln L}$ and $\frac{\mathcal{F} }{\ln t}$ and call them fidelity and echo exponents respectively.

@@

Next, we analyze the more interesting $\theta$ dependent process ${\rm DN} \rightarrow \lambda$
%in Eq.~\eqref{eq:DNDN}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. We worked with a system containing $35000$ sites. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
where we have used the full notation as in Eq.~\eqref{eq:Full_notation_rand()}. Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. %We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) for the process $\text{DN} \rightarrow \lambda$ {\iffalse in Eq.~\eqref{eq:DNDN}\fi}. The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

We finally consider the process $\text{P} \rightarrow \lambda$
% in Eq.~\eqref{eq:PP}
%\begin{equation}
%\text{P}+\text{P}\rightarrow\lambda+\text{P},
%\end{equation}
in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
\begin{equation}
\begin{aligned}
\label{eq:approx_PPPP}
S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
\end{aligned}
\end{equation}
where $\delta\theta=0.003\pi$. The $\theta$ dependent exponents are now symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
    \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for the process $\text{P} \rightarrow \lambda${\iffalse in Eq.~\eqref{eq:PP}\fi}. The parameters are the same as those in Fig.~\ref{fig:DDNN}. The plot is symmetric with respect to $\theta=0.25\pi$ as predicted. The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text. Inset in (a): From top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
    \label{fig:PPPP}
\end{figure}

Finally, we also provide the data for the process
\begin{equation}
\label{eq:DNP_rand()}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at large value of $\theta$. The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo for the process in Eq.~\eqref{eq:DNP_rand()}. The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}

>>>>

We use the lattice model introduced in Sec.~\ref{sec_sub:free_boson_lattice} to check the analytic results. Our numerical calculations are based on a boson Bogoliubov transformation and the explicit form of the groundstates. The readers are referred to App.~\ref{app:comp_fid_echo} for the technical details. In all the figures, we present the coefficients of the logarithmic term $\frac{\mathcal{F}}{\ln L}$ and $\frac{\mathcal{F} }{\ln t}$ and call them fidelity and echo exponents respectively.

@@

Next, we analyze the more interesting $\theta$ dependent process ${\rm DN} \rightarrow \lambda$
%in Eq.~\eqref{eq:DNDN}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the boundary condition after joining is determined by $S_1(\theta)$. We worked with a system containing $35000$ sites. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: the exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process (see the full notation in Eq.~\eqref{eq:Full_notation_rand()})
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta).
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of the power law decay, and the corresponding exponents follow the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. %We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for (a) the Loschmidt echo and (b) the bipartite fidelity of the process $\text{DN} \rightarrow \lambda$. {\iffalse in Eq.~\eqref{eq:DNDN}\fi} The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of the Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described in Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

We finally consider the process $\text{P} \rightarrow \lambda$
% in Eq.~\eqref{eq:PP}
%\begin{equation}
%\text{P}+\text{P}\rightarrow\lambda+\text{P},
%\end{equation}
in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
\begin{equation}
\begin{aligned}
\label{eq:approx_PPPP}
S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
\end{aligned}
\end{equation}
where $\delta\theta=0.003\pi$. The $\theta$ dependent exponents are now symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance with Eq.~\eqref{eq:periodic-case}.

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
    \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
    \caption{The decay exponent of (a) the Loschmidt echo and (b) the bipartite fidelity of the process $\text{P} \rightarrow \lambda$.{\iffalse in Eq.~\eqref{eq:PP}\fi} The parameters are the same as those in Fig.~\ref{fig:DDNN}. The plot is symmetric with respect to $\theta=0.25\pi$ as predicted. The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text. Inset in (a): From top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
    \label{fig:PPPP}
\end{figure}

Finally, we also provide the data for the process
\begin{equation}
\label{eq:DNP_rand()}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at large value of $\theta$. The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of the Loschmidt echo for the process in Eq.~\eqref{eq:DNP_rand()}. The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$.}
\label{fig:PDN_fit}
\end{figure}

### 2017-10-14 pf_of_id.tex
[referee] version resubmitted to prb.

In this appendix, we provide more details for calculating the amplitude $Z_{ab}$ in Sec.~\ref{sec:analytic_numerics}. We start to prove the following identity for a real symmetric matrix $M$
\begin{equation}
\label{eq:first_id_app_pf_of_id}
e^{- \vec{b}^{\dagger} M \vec{b} } e^{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger} }  = e^{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger} } e^{- \vec{b}^{\dagger} M \vec{b} } ,
%\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
\end{equation}
where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators. The matrix notation here should be understand as a bilinear expression. For example, $\vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}$ should really mean $\sum_{ij}b^\dagger_iR_{ij}\bar{b}_j^\dagger$ where the dagger does not transpose the vector.

@@

A direct consequence of Eq.~\eqref{eq:first_id_app_pf_of_id} is the following
\begin{equation}
\label{eq:second_id_in_app_pf_of_id}
Z_{ab} = \langle 0 | e^{ \vec{b} R_a^* \vec{\bar{b}} } e^{ - \vec{b}^{\dagger} M  \vec{b} } e^{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger} }  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )} ,
%Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )} 
\end{equation}
where $|0\rangle$ is the vacuum for ${\bf b}$ and $\bar{\bf b}$. Using the identity we have just proved
\begin{equation}
Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle ,
\end{equation}
a direct application of the MacMahon master theorem
\begin{equation}
  \langle 0 | \exp \Big\{ \vec{b}_1 X \vec{b}_2 \Big\}  \exp \Big\{ \vec{b}^{\dagger}_1 Y \vec{b}^{\dagger}_2 \Big\}|0  \rangle 
 = \frac{1}{\det(1 - X^T Y )}
\end{equation}
proves Eq.~\eqref{eq:second_id_in_app_pf_of_id}. \hfill$\blacksquare$

>>>>

In this appendix, we provide more details for calculating the amplitude $Z_{ab}$ in Sec.~\ref{sec:analytic_numerics}. We start to prove the following identity for a real symmetric matrix $M$
\begin{equation}
\label{eq:first_id_app_pf_of_id}
e^{- \vec{b}^{\dagger} M \vec{b} } e^{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger} }  = e^{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger} } e^{- \vec{b}^{\dagger} M \vec{b} } ,
%\exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} \exp \Big\{ \vec{b}^{\dagger} R \bar{\vec{b}}^{\dagger}  \Big\}  = \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R \bar{\vec{b}}^{\dagger}  \Big\} \exp\Big\{- \vec{b}^{\dagger} M \vec{b}  \Big\} 
\end{equation}
where ${\bf b}$ and $\bar{\bf b}$ are vectors of bosonic operators. The matrix notation here should be understood as a bilinear expression as explained below Eq.~\eqref{eq:bd_state_matrix}.

@@

A direct consequence of Eq.~\eqref{eq:first_id_app_pf_of_id} is the following
\begin{equation}
\label{eq:second_id_in_app_pf_of_id}
Z_{ab} = \langle 0 | e^{ \vec{b} R_a^* \vec{\bar{b}} } e^{ - \vec{b}^{\dagger} M  \vec{b} } e^{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger} }  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )} ,
%Z_{ab} = \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\} \exp\Big\{ - \vec{b}^{\dagger} M  \vec{b} \Big\}   \exp\Big\{  \vec{b}^{\dagger} R_b  \vec{\bar{b}}^{\dagger}\Big\}  |0  \rangle  = \frac{1}{\det( 1- R_a^{\dagger} e^{-M} R_b )} 
\end{equation}
where $|0\rangle$ is the vacuum for ${\bf b}$ and $\bar{\bf b}$.

One can use the identity in Eq.~\eqref{eq:first_id_app_pf_of_id} to reduce $Z_{ab}$ to 
\begin{equation}
Z_{ab} =   \langle 0 | \exp\Big\{ \vec{b} R_a^* \vec{\bar{b}}\Big\}  \exp \Big\{ \vec{b}^{\dagger} e^{-M}  R_b \bar{\vec{b}}^{\dagger}  \Big\}  |0 \rangle, 
\end{equation}
then a direct application of the MacMahon master theorem
\begin{equation}
  \langle 0 | \exp \Big\{ \vec{b}_1 X \vec{b}_2 \Big\}  \exp \Big\{ \vec{b}^{\dagger}_1 Y \vec{b}^{\dagger}_2 \Big\}|0  \rangle 
 = \frac{1}{\det(1 - X^T Y )}
\end{equation}
proves Eq.~\eqref{eq:second_id_in_app_pf_of_id}. \hfill$\blacksquare$
